---
title: "Installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

After the usual R package installation, `torch` requires installing other 2 libraries: LibTorch and LibLantern. They are automatically installed by detecting information about you OS if you are using `torch` in interactive mode. If you are running `torch` in non-interactive environments you need to set the `TORCH_INSTALL` env var to 1, so it's automatically installed or manually call `torch::install_torch()`.

We have provide pre-compiled binaries for all major platforms and you can find specific installation instructions below.

## Windows

### CPU

If you don't have a GPU or want to install the CPU version of `torch`, you can install with:

```{r}
install.packages("torch")
```

Some Windows distributions don't have the Visual Studio runtime pre-installed and you will observe an error like:

    Error in cpp_lantern_init(normalizePath(install_path())): C:\Users\User\Documents\R\R-4.0.2\library\torch\deps\lantern.dll - The specified module could not be found.

See [here](https://github.com/mlverse/torch/issues/246#issuecomment-695097121) for instructions on how to install it.

### GPU

Since version 0.1.1 torch supports GPU installation on Windows. In order to use GPU's with torch you need to:

-   Have a CUDA compatible NVIDIA GPU. You can find if you have a CUDA compatible GPU [here](https://developer.nvidia.com/cuda-gpus#compute).

-   Have properly installed the NVIDIA CUDA toolkit versions 10.1 or 10.2. For CUDA v10.2, follow the installation instructions [here](https://docs.nvidia.com/cuda/archive/10.2/cuda-installation-guide-microsoft-windows/index.html). **Note**: We currently do **not** support the latest CUDA version 11.

-   Have installed cuDNN version 7.6 (for the correct CUDA version). Follow the installation instructions available [here](https://docs.nvidia.com/deeplearning/cudnn/archives/cudnn_765/cudnn-install/index.html). **Note:** latest cuDNN version 8 is not yet supported.

Once you have installed all pre-requisites you can install `torch` with:

```{r}
install.packages("torch")
```

If you have followed default installation locations we will detect that you have CUDA software installed and automatically download the GPU enabled Lantern binaries. You can also specify the `CUDA` env var with something like `Sys.setenv(CUDA="10.1")` if you want to force an specific version of the CUDA toolkit.

## MacOS

### CPU

We only support CPU builds of torch on MacOS. On MacOS you can install torch with:

```{r}
install.packages("torch")
```

## Linux

### CPU

To install the cpu version of `torch` you can run:

```{r}
install.packages("torch")
```

### GPU

To install the GPU version of `torch` on linux you must verify that:

-   You have a NVIDIA CUDA compatible GPU. You can find if you have a CUDA compatible GPU [here](https://developer.nvidia.com/cuda-gpus#compute).

-   You have correctly installed the NVIDIA CUDA Toolkit versions 10.1 or 10.2, follow the instructions [here](https://docs.nvidia.com/cuda/archive/10.2/cuda-installation-guide-linux/index.html). **Note**: We currently do **not** support the latest CUDA version 11.

-   You have installed cuDNN version 7.6 (for the correct CUDA version). Follow the installation instructions available [here](https://docs.nvidia.com/deeplearning/cudnn/archives/cudnn_765/cudnn-install/index.html#install-linux). **Note:** latest cuDNN version 8 is not yet supported.

Once you have installed all pre-requisites you can install `torch` with:

```{r}
install.packages("torch")
```

If you have followed default installation locations we will detect that you have CUDA software installed and automatically download the GPU enabled Lantern binaries. You can also specify the `CUDA` env var with something like `Sys.setenv(CUDA="10.1")` if you want to force an specific version of the CUDA toolkit.
