---
title: "Creating tensors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating tensors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(torch)
```

In this article we describe all the possibilities available to create `torch` 
tensors in R.

## From R objects

You can create tensors from R objects using the `torch_tensor` function. The 
`torch_tensor` function takes R a vector, matrix or array and creates a `torch_tensor`
with the data.

You can see a few examples below:

```{r}
torch_tensor(c(1,2,3))
torch_tensor(matrix(1:10, ncol = 5, nrow = 2))
torch_tensor(array(runif(12), dim = c(2, 2, 3)))
```

Note that by default we will create tensors in the `cpu` device and that we will
convert their numeric to the corresponding torch `dtype`.

> **Note** currently, only numeric and boolean types are supported.

You can always modify the dtype and the device when converting an R object to 
a torch tensor. For example:

```{r}
torch_tensor(1, dtype = torch_long())
torch_tensor(1, device = torch_device("cpu"), dtype = torch_float64())
```

Other options available when creating a tensor are:

- `requires_grad`: boolean indicating if you want `autograd` to record operations 
  on them for automatic differentiation.
- `pin_memmory`: – If set, returned tensor would be allocated in the pinned memory. 
  Works only for CPU tensors.
  
These options are available for all functions that can be used to create new tensors,
including the factory functions listed in the next section.

## Using creation functions

You can also use the `torch_*` functionslisted below to create torch tensors 
using some algorithm. 

For example, the `torch_randn` function will create tensors using the normal 
distribution with mean equals to 0 and standard deviation equals 1. You can
use the `...` to pass the size of the dimensions, ie, the code below will 
create a normally distributed tensor with shape 5x3.

```{r}
x <- torch_randn(5, 3)
x
```

Another example is the `torch_ones` function, which creates a tensor filled with 
ones.

```{r}
x <- torch_ones(2, 4, dtype = torch_int64(), device = "cpu")
x
```

Here is the full list of functions that can be used to create tensors in torch:

- `torch_arange`: Returns a tensor with a sequence of integers,
- `torch_empty`: Returns a tensor with uninitialized values,
- `torch_eye`: Returns an identity matrix,
- `torch_full`: Returns a tensor filled with a single value,
- `torch_linspace`: Returns a tensor with values linearly spaced in some interval,
- `torch_logspace`: Returns a tensor with values logarithmically spaced in some interval,
- `torch_ones`: Returns a tensor filled with all ones,
- `torch_rand`: Returns a tensor filled with values drawn from a uniform distribution on [0, 1).
- `torch_randint`: Returns a tensor with integers randomly drawn from an interval,
- `torch_randn`: Returns a tensor filled with values drawn from a unit normal distribution,
- `torch_randperm`: Returns a tensor filled with a random permutation of integers in some interval,
- `torch_zeros`: Returns a tensor filled with all zeros.

## Convertion

Once a tensor exists you can convert it between dtypes and move to different 
devices with to `to` method. For example:

```{r}
x <- torch_tensor(1)
y <- x$to(dtype = torch_int32())
x
y
```

You can also copy a tensor the GPU using:

```{r, eval = FALSE}
x <- torch_tensor(1)
y <- x$to(torch_device("cuda"))
```

