---
title: "TorchScript"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TorchScript}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = identical(Sys.getenv("TORCH_TEST", unset = "0"), "1")
)
```

```{r setup}
library(torch)
```

[TorchScript](https://pytorch.org/docs/stable/jit_language_reference.html#language-reference) is a statically typed subset of Python that can be interpret by LibTorch without any Python dependency. TorchScript programs can be created from R using tracing. When using tracing, code is automatically converted into this subset of Python by recording only the actual operators on tensors and simply executing and discarding the other surrounding R code.

The R package can also execute TorchScript programs created in Python (or other languages). They are loaded `jit_load()` and seem like usual `nn_module()` objects.

## Types

The following table lists all TorchScript types and how to convert the to and back to R.

| TorchScript Type          | R Description                                                                         |
|---------------------------|---------------------------------------------------------------------------------------|
| `Tensor`                  | A `torch_tensor` with any shape, dtype or backend.                                    |
| `Tuple[T0, T1, ..., TN]`  | A `list()` containing subtypes `T0`, `T1`, etc. wrapped with `jit_tuple()` .          |
| `bool`                    | A scalar logical value create using `jit_scalar`.                                     |
| `int`                     | A scalar integer value created using `jit_scalar`.                                    |
| `float`                   | A scalar floating value created using `jit_scalar`.                                   |
| `str`                     | A string (ie. character vector of length 1) wrapped in `jit_scalar`.                  |
| `List[T]`                 | An R list of which all types are type `T` . Or numeric vectors, logical vectors, etc. |
| `Optional[T]`             | Not yet supported.                                                                    |
| `Dict[str, V]`            | A named list with values of type `V` . Only `str` key values are currently supported. |
| `T`                       | Not yet supported.                                                                    |
| `E`                       | Not yet supported.                                                                    |
| `NamedTuple[T0, T1, ...]` | A named list containing subtypes `T0`, `T1`, etc. wrapped in `jit_tuple()`.           |

## Creating TorchScript programs

Currently the only supported way to create TorchScript programs from R is using tracing.

See `?jit_trace` for documentation on tracing.

## Executing TorchScript programs

TorchScript programs can be loaded from disk using `jit_load()` and later executed.

The loaded programs are represented by a `ScriptModule` that behaves similar to `nn_module()`s.

R objects are automatically converted to their TorchScript counterpart following the Types table in this document. However, sometimes it's necessary to make type annotations with `jit_tuple()` and `jit_scalar()` to disambiguate the conversion.
