---
title: 'nn: neural networks with torch'
type: docs
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = identical(Sys.getenv("TORCH_TEST", unset = 0), 1)
)
```

> Note: This is an R port of the official tutorial available [here](https://pytorch.org/tutorials/beginner/examples_tensor/two_layer_net_numpy.html#sphx-glr-beginner-examples-tensor-two-layer-net-numpy-py). All credits goes to [Justin Johnson](https://github.com/jcjohnson/pytorch-examples).

```{r setup}
library(torch)
```

Computational graphs and autograd are a very powerful paradigm for defining complex operators and automatically taking derivatives; however for large neural networks raw autograd can be a bit too low-level.

When building neural networks we frequently think of arranging the computation into layers, some of which have learnable parameters which will be optimized during learning.

In TensorFlow, packages like Keras, TensorFlow-Slim, and TFLearn provide higher-level abstractions over raw computational graphs that are useful for building neural networks.

In torch, the nn functionality serves this same purpose. The nn feature defines a set of Modules, which are roughly equivalent to neural network layers. A Module receives input Tensors and computes output Tensors, but may also hold internal state such as Tensors containing learnable parameters. The nn collection also defines a set of useful loss functions that are commonly used when training neural networks.

In this example we use nn to implement our two-layer network:

```{r}
if (cuda_is_available()) {
   device <- torch_device("cuda")
} else {
   device <- torch_device("cpu")
}
   
# N is batch size; D_in is input dimension;
# H is hidden dimension; D_out is output dimension.
N <- 64
D_in <- 1000
H <- 100
D_out <- 10

# Create random input and output data
# Setting requires_grad=FALSE (the default) indicates that we do not need to 
# compute gradients with respect to these Tensors during the backward pass.
x <- torch_randn(N, D_in, device=device)
y <- torch_randn(N, D_out, device=device)

# Use the nn package to define our model as a sequence of layers. nn_sequential
# is a Module which contains other Modules, and applies them in sequence to
# produce its output. Each Linear Module computes output from input using a
# linear function, and holds internal Tensors for its weight and bias.
model <- nn_sequential(
    nn_linear(D_in, H),
    nn_relu(),
    nn_linear(H, D_out)
)

# The nn package also contains definitions of popular loss functions; in this
# case we will use Mean Squared Error (MSE) as our loss function.
loss_fn <- nnf_mse_loss

learning_rate <- 1e-6
for (t in seq_len(500)) {
   # Forward pass: compute predicted y by passing x to the model. Module objects
   # can be called like functions. When doing so you pass a Tensor of input
   # data to the Module and it produces a Tensor of output data.
   y_pred <- model(x)
   
   # Compute and print loss. We pass Tensors containing the predicted and true
   # values of y, and the loss function returns a Tensor containing the
   # loss.
   loss <- loss_fn(y_pred, y)
   if (t %% 100 == 0 || t == 1)
      cat("Step:", t, ":", as.numeric(loss), "\n")
   
   # Zero the gradients before running the backward pass.
   model$zero_grad()

   # Backward pass: compute gradient of the loss with respect to all the learnable
   # parameters of the model. Internally, the parameters of each Module are stored
   # in Tensors with requires_grad=TRUE, so this call will compute gradients for
   # all learnable parameters in the model.
   loss$backward()
   
   # Update the weights using gradient descent. Each parameter is a Tensor, so
   # we can access its gradients like we did before.
   with_no_grad({
      for (param in model$parameters) {
         param$sub_(learning_rate * param$grad)
      }
   })
}
```

In the [next example](optim.html) we will learn how to use optimizers implemented in torch.
