---
title: 'optim: optimizers in torch'
type: docs
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = identical(Sys.getenv("TORCH_TEST", unset = "0"), "1")
)
```

> Note: This is an R port of the official tutorial available [here](https://pytorch.org/tutorials/beginner/examples_tensor/two_layer_net_numpy.html#sphx-glr-beginner-examples-tensor-two-layer-net-numpy-py). All credits goes to [Justin Johnson](https://github.com/jcjohnson/pytorch-examples).

```{r setup}
library(torch)
```

Up to this point we have updated the weights of our models by manually mutating the Tensors holding learnable parameters (with `with_no_grad` to avoid tracking history in autograd). This is not a huge burden for simple optimization algorithms like stochastic gradient descent, but in practice we often train neural networks using more sophisticated optimizers like AdaGrad, RMSProp, Adam, etc.

The optim package in torch abstracts the idea of an optimization algorithm and provides implementations of commonly used optimization algorithms.

In this example we will use the nn package to define our model as before, but we will optimize the model using the Adam algorithm provided by `optim`:

```{r}
if (cuda_is_available()) {
   device <- torch_device("cuda")
} else {
   device <- torch_device("cpu")
}
   
# N is batch size; D_in is input dimension;
# H is hidden dimension; D_out is output dimension.
N <- 64
D_in <- 1000
H <- 100
D_out <- 10

# Create random input and output data
# Setting requires_grad=FALSE (the default) indicates that we do not need to 
# compute gradients with respect to these Tensors during the backward pass.
x <- torch_randn(N, D_in, device=device)
y <- torch_randn(N, D_out, device=device)

# Use the nn package to define our model as a sequence of layers. nn_sequential
# is a Module which contains other Modules, and applies them in sequence to
# produce its output. Each Linear Module computes output from input using a
# linear function, and holds internal Tensors for its weight and bias.
model <- nn_sequential(
    nn_linear(D_in, H),
    nn_relu(),
    nn_linear(H, D_out)
)

# The nn package also contains definitions of popular loss functions; in this
# case we will use Mean Squared Error (MSE) as our loss function.
loss_fn <- nnf_mse_loss

# Use the optim package to define an Optimizer that will update the weights of
# the model for us. Here we will use Adam; the optim package contains many other
# optimization algorithms. The first argument to the Adam constructor tells the
# optimizer which Tensors it should update.
learning_rate <- 1e-4
optimizer <- optim_adam(model$parameters, lr=learning_rate)

for (t in seq_len(500)) {
   # Forward pass: compute predicted y by passing x to the model. Module objects
   # can be called like functions. When doing so you pass a Tensor of input
   # data to the Module and it produces a Tensor of output data.
   y_pred <- model(x)
   
   # Compute and print loss. We pass Tensors containing the predicted and true
   # values of y, and the loss function returns a Tensor containing the
   # loss.
   loss <- loss_fn(y_pred, y)
   if (t %% 100 == 0 || t == 1)
      cat("Step:", t, ":", as.numeric(loss), "\n")
   
   # Before the backward pass, use the optimizer object to zero all of the
   # gradients for the variables it will update (which are the learnable
   # weights of the model). This is because by default, gradients are
   # accumulated in buffers( i.e, not overwritten) whenever $backward()
   # is called. Checkout docs of `autograd_backward` for more details.
   optimizer$zero_grad()

   # Backward pass: compute gradient of the loss with respect to model
   # parameters
   loss$backward()

   # Calling the step function on an Optimizer makes an update to its
   # parameters
   optimizer$step()
}
```

In the [next example](custom-nn.html) we will learn how to create custom `nn_modules`.
